%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{xcolor}
\newcommand\invisible[1]{\textcolor{white}{\fontsize{0}{0}#1}}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage[hidelinks]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Tushar Gahlaut} % Your name
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{+91 9717562252 \\ \href{mailto:tushargahlaut74@gmail.com}{tushargahlaut74@gmail.com} \\ \href{https://www.linkedin.com/in/tushargahlaut/}{LinkedIn} \\ \href{https://github.com/tushargahlaut}{GitHub} \\ \href{https://leetcode.com/TUsharGahlaut}{LeetCode}}  %


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Profile Summary}

{\normalfont I am a skilled Software Engineer with 2 Years of Experience developing and maintaining scalable applications using \textbf{Modern Software  Technologies and Frameworks, Cloud Platforms and Generative AI Services}.}

\end{rSection}




%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}

\textbf{Programming Languages}: {\normalfont C++, Javascript, Typescript, Java, Python.}
\\
\textbf{Frameworks/Libraries}: {\normalfont ReactJs, NodeJs, FastAPI, Jest, Spring Framework, JUnit, Mockito.}
 \\
 \textbf{Databases}: {\normalfont MongoDB, Azure CosmosDB, SQL, Redis, Azure Blob Storage}
 \\
 \textbf{DevOps and Cloud}: {\normalfont Microsoft Azure, Docker, Kubernetes, OpenShift, GitHub Actions}
 \\
 \textbf{Message Brokers and Analytics}: {\normalfont Kafka, AMQ Streams, Elasticsearch, Azure App Insights}  
\\ \textbf{Core CS Subjects}: {\normalfont Data Structures and Algorithms, Operating Systems, Computer Networks, DBMS, OOPs}
% \textbf{API and Development Tools}: {\normalfont REST, GraphQL, Visual Studio Code, Postman, GitHub, PyCharm, CoPilot}
\end{rSection}




%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------




\begin{rSection}{WORK EXPERIENCE}

{\bf Software Development Engineer - IndiGo  \hfill July 2023 - Present }
\begin{itemize}
\item{\normalfont{ \textbf{6Eskai} - A GenAI powered Chatbot for Customer Experience }}
\begin{itemize}
    \item {\normalfont Developed \textbf{6Eskai} using \textbf{React.js and FastAPI} to implement real-time response streaming, also developed features such as \normalfont{Flight Booking, Boarding Pass} and \textbf{Juspay Payment Integration}.}
    \item {\normalfont Led migration of IndiGo's legacy Yellow Messenger live agent to \textbf{Salesforce's} services. Integrated \normalfont{Server-Sent Events} and \normalfont{Streaming Responses} with \textbf{Python FastAPI}.}
    \item {\normalfont Integrated \textbf{Microsoft Azure AI Services} like \textbf{Semantic Search, Document Intelligence etc} and \textbf{Azure Cosmos DB} for building 6Eskai's Knowledge Base to answer customer's related queries.}
    \item{ \normalfont{Engineered \textbf{Cron Jobs} to automate knowledge base updates and implemented PII-compliant chat storage in \textbf{Azure Cosmos DB}.} }
\end{itemize}

    % \item{\normalfont Integrated \normalfont{Navitaire} APIs and \textbf{Microservices} on 6Eskai for widely used features like Flight Booking, Boarding Pass, Web Check-In, Plan B, Seat Selection and many more.}

    % \item {\normalfont Integrated \textbf{Microsoft Azure AI Services} like \normalfont{Semantic Search, Document Intelligence etc} and \textbf{Azure Cosmos DB} for building 6Eskai's Knowledge Base to answer customer's related queries.}
    % \item {\normalfont Implemented \textbf{CI/CD} Pipelines using \textbf{GitHub Actions} on Openshift and Azure, automated deployment of internal applications written using \textbf{Java Spring Framework}.}
\end{itemize}
\begin{itemize}
    \item {\normalfont \textbf{6E Elevate} - Integrating Leadership Engagement and Employee Incentive Programs.}
    \begin{itemize}
        \item {\normalfont Developed 6E Elevate platform using \textbf{Java Spring Boot} and \normalfont{React.js}, enabling video streaming from Azure Blob Storage and \textbf{OAuth2} based employee authentication.}
        \item {\normalfont Implemented \textbf{CI/CD} Pipelines using \textbf{GitHub Actions} to automate deployment of this application.}
    \end{itemize}
\end{itemize}

{\bf Frontend Tech Consultant - Kurage {\normalfont \emph{(Internship)}}  \hfill August 2022 - January 2023 }
\begin{itemize}

    \item {\normalfont Built Frontend for MORF and SKG websites using \textbf{Next.js}, implemented state management using 
 \textbf{Redux Toolkit} and \textbf{Google Auth} for secure Authentication.}
   \item {\normalfont Integrated APIs using \textbf{{Apollo GraphQL}} for data querying and mutation operations like fetching Product Details, handling File Uploads to \textbf{AWS S3 Buckets} , User Auth through \textbf{Google Sign In} etc.} 
\end{itemize}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology in Computer Science and Engineering} \hfill {2019 - 2023}
\\ 
{\normalfont Guru Gobind Singh Indraprastha University, New Delhi}, \textbf{CGPA : 9.1/10}

\end{rSection}




 
%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------


\begin{rSection}{Projects}
   \begin{itemize}
    \item \textbf{Trade Vibes} 
    \href{https://github.com/tushargahlaut/TradeVibes}
    {\emph{(Link)}}
    \\ \textbf{Technologies Used}: MERN Stack, Redis, Cloudinary, Typescript, Shadcn/ui, Docker, Openshift.
     \\An online platform for discussing stock market trends and sharing investment knowledge. Did integration of APIs from NSE India website for Nifty 50 data and Redis for caching.
   %  \item \textbf{Talk Spot} 
   % \href{https://github.com/tushargahlaut/talkspot-chat-app}{\emph{(Link)}} 
   % \\ \textbf{Technologies Used}: NextJS, Redux Toolkit, Cloudinary, NodeJS, ExpressJS, MongoDB, Socket.io 
   % \\{\normalfont A real time chat website which allows users to create 1-1 and group chat rooms to send/receive messages.}
   
   \end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS AND CERTIFICATES
%----------------------------------------------------------------------------------------

% \begin{rSection}{Extracurricular Activities}

% \begin{itemize}
%    \item {Smart India Hackathon 2022 National Finalist} - {\normalfont Developed a platform to bring together multiple programming resources for students.}{\normalfont (\href{https://drive.google.com/file/d/1No-u1sUaclG-nf7_Gtym5JDEz1ydyRSL/view?usp=sharing}{\emph{Certificate}})}

%  % \invisible{lorem}
% \end{itemize}
% \end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATES
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------



\end{document}

